ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
fixing typos on page 4
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

In order to check the aforementioned properties, ESBMC-GPU explicitly explores the possible interleavings (up to the given context bound) and calls the single-threaded BMC procedure on each one, whenever it reaches an RT leaf node. Then, the mentioned procedure will stop if it finds a bug or when all possible RT interleavings has been systematically explored~\cite{pereira:2016}.

@@

In the mentioned example, ESBMC-GPU detects an array out-of-bounds violation. Indeed, this CUDA-based program retrieves a memory region that has not been previously allocated, {\it i.e.}, when {\tt threadIdx.x = 1}, the program tries to access $a[2]$. Importantly, the {\tt cudaMalloc()} function's operational model has a precondition that checks if the memory size to be allocated is greater than zero. In addition, an assertion checks if the result matches to the expected postcondition (line $19$). Therefore, the verification of this program through ESBMC-GPU produces $54$ successful and $3$ failed interleavings. For instance, one possible failed interleaving is represented by the threads executions $t_0 : a[1] = 0$; $t_1 : a[2] = 1$, where $a[2] = 1$ represents an incorrect access to the array index $a$. It is worth noticing that CIVL, ESBMC-GPU, and GKLEE are also able to detect this array out-of-bounds violation, but GPUVerify fails, as it reports a true incorrect result (missed bug).

>>>>

In order to check the aforementioned properties, ESBMC-GPU explicitly explores the possible interleavings (up to the given context bound) and calls the single-threaded BMC procedure on each one, whenever it reaches an RT leaf node. Then, the mentioned procedure will stop if it finds a bug or when all possible RT interleavings have been systematically explored~\cite{pereira:2016}.

@@

In the mentioned example, ESBMC-GPU detects an array out-of-bounds violation. Indeed, this CUDA-based program retrieves a memory region that has not been previously allocated, {\it i.e.}, when {\tt threadIdx.x = 1}, the program tries to access $a[2]$. Importantly, the {\tt cudaMalloc()} function's operational model has a precondition that checks if the memory size to be allocated is greater than zero. In addition, an assertion checks if the result matches to the expected postcondition (line $19$). The verification of this program through ESBMC-GPU produces $54$ successful and $3$ failed interleavings. For instance, one possible failed interleaving is represented by the threads executions $t_0 : a[1] = 0$; $t_1 : a[2] = 1$, where $a[2] = 1$ represents an incorrect access to the array index $a$. It is worth noticing that CIVL, ESBMC-GPU, and GKLEE are also able to detect this array out-of-bounds violation, but GPUVerify fails, as it reports a true incorrect result (missed bug).
